### 2012-06-01 docs/SDC/sdc.tex
sdc updates

\subsection{Species Source Terms.}
For the species prediction, the form of $I$ depends on
{\tt species\_pred\_type} (see \S \ref{sec:pred:density}).
We note that there is no $I$ term for $\rho$ or $\rho'$ prediction, since
the density evolution equation does not have a reaction source term.
\begin{itemize}
\item {\tt species\_pred\_type} = 1 (predict $\rho'$ and $X_k$) 
or 3 (predict $\rho$ and $X_k$)

\begin{equation}
I_{X_k} = \frac{1}{\rho^{n+\myhalf}} \left [ 
      \frac{(\rho X_k)^\mathrm{new} - 
            (\rho X_k)^\mathrm{old}}{\Delta t} - A_{\rho X_k}  \right ].
\end{equation}
(Andy's Idea) Define $I_{X_k}$ using
\begin{equation}
I_{X_k} = \frac{X_k^\mathrm{new} - X_k^\mathrm{old}}{\Delta t} - A_{X_k},
\end{equation}
where we first define a state that has only been updated with advection:
\begin{equation}
\frac{(\rho X_k)^{(1)} - (\rho X_k)^\mathrm{old}}{\Delta t} = A_{\rho X_k},
\end{equation}
and then define the species mass fractions,
\begin{equation}
X_k^{(1)} = (\rho X_k)^{(1)} / \sum_k (\rho X_k)^{(1)}, \quad 
X_k^\mathrm{old} = (\rho X_k)^\mathrm{old} / \sum_k (\rho X_k)^\mathrm{old}, \quad 
X_k^\mathrm{new} = (\rho X_k)^\mathrm{new} / \sum_k (\rho X_k)^\mathrm{new},
\end{equation}
and finally define $A_{X_k}$ using
\begin{equation}
\frac{X^{(1)} - X^\mathrm{old}}{\Delta t}= A_{X_k}.
\end{equation}
\item {\tt species\_pred\_type} = 2 (predict $\rho'$ and $(\rho X_k)$)
\begin{equation}
I_{\rho X_k} = \frac{(\rho X_k)^\mathrm{new} - (\rho X_k)^\mathrm{old}}{\Delta t} - A_{\rho X_k}.
\label{eq:sdc:Irhoo}
\end{equation}
\end{itemize}

@@

\begin{itemize}
\item {\tt enthalpy\_pred\_type} = {\tt predict\_rhohprime} (not implemented yet)

@@

\item {\tt enthalpy\_pred\_type} = {\tt predict\_h}

@@

\item {\tt enthalpy\_pred\_type} = {\tt predict\_T\_then\_rhoprime} or 
      {\tt enthalpy\_pred\_type} = {\tt predict\_T\_then\_h}

>>>>

\subsection{Species Source Terms.}
For the species prediction, the form of $I$ depends on
{\tt species\_pred\_type} (see \S \ref{sec:pred:density}).
We note that there is no $I$ term for $\rho$ or $\rho'$ prediction, since
the density evolution equation does not have a reaction source term.
\begin{itemize}
\item {\tt species\_pred\_type} = 1 ({\tt predict\_rhoprime\_and\_X})
or 3 ({\tt predict\_rho\_and\_X})

\begin{equation}
I_{X_k} = \frac{1}{\rho^{n+\myhalf}} \left [ 
      \frac{(\rho X_k)^\mathrm{new} - 
            (\rho X_k)^\mathrm{old}}{\Delta t} - A_{\rho X_k}  \right ].
\end{equation}
(Andy's Idea) Define $I_{X_k}$ using
\begin{equation}
I_{X_k} = \frac{X_k^\mathrm{new} - X_k^\mathrm{old}}{\Delta t} - A_{X_k},
\end{equation}
where we first define a state that has only been updated with advection:
\begin{equation}
\frac{(\rho X_k)^{(1)} - (\rho X_k)^\mathrm{old}}{\Delta t} = A_{\rho X_k},
\end{equation}
and then define the species mass fractions,
\begin{equation}
X_k^{(1)} = (\rho X_k)^{(1)} / \sum_k (\rho X_k)^{(1)}, \quad 
X_k^\mathrm{old} = (\rho X_k)^\mathrm{old} / \sum_k (\rho X_k)^\mathrm{old}, \quad 
X_k^\mathrm{new} = (\rho X_k)^\mathrm{new} / \sum_k (\rho X_k)^\mathrm{new},
\end{equation}
and finally define $A_{X_k}$ using
\begin{equation}
\frac{X^{(1)} - X^\mathrm{old}}{\Delta t}= A_{X_k}.
\end{equation}
\item {\tt species\_pred\_type} = 2 ({\tt predict\_rhoX})
\begin{equation}
I_{\rho X_k} = \frac{(\rho X_k)^\mathrm{new} - (\rho X_k)^\mathrm{old}}{\Delta t} - A_{\rho X_k}.
\label{eq:sdc:Irhoo}
\end{equation}
\end{itemize}

@@

\begin{itemize}
\item {\tt enthalpy\_pred\_type} = 1 ({\tt predict\_rhohprime}, not implemented yet)

@@

\item {\tt enthalpy\_pred\_type} = 2 ({\tt predict\_h} )

@@

\item {\tt enthalpy\_pred\_type} = 3 ({\tt predict\_T\_then\_rhoprime}) or 
      {\tt enthalpy\_pred\_type} = 4 ({\tt predict\_T\_then\_h} )
